Poseidon Adventure

### 2021-05-25 docs/index.Rmd
initial per capita consumption testing

@@

>>>>

### Diagnosing diet and consumption outputs, May 2021

<a href="https://noaa-edab.github.io/poseidon-dev/PerCapitaConsumption.html" target="_blank"> Compare NOBA and CCA consumption outputs, May 25, 2021</a>

@@

Code converting these outputs to multispecies production model and length structured model inputs is in development as of spring 2021 and is on the [ms-keyrun repository](https://github.com/NOAA-EDAB/ms-keyrun/blob/master/docs/SimData.Rmd). See also <a href="https://noaa-edab.github.io/ms-keyrun/SimData.html" target="_blank"> Initial simulated data, May 24, 2021</a>
